Turbo fast no compromise gravitational wave parameter estimation

### 2022-11-21 src/tex/ms.tex
update

\begin{align}
    \log{\mathcal{L}(d|\theta)} = -\left<d-h(\mathbf{\theta})|d-h(\mathbf{\theta})\right>/2,
\end{align}

where $d$ is the data, $h(\mathbf{\theta})$ is the strain predicted by a waveform model with a specific set of source parameters.
It is computationally cheaper to compute the likelihood in the frequency domain, which can be defined as 
\begin{align}
    \left<a|b\right> = 4 Re\int \frac{a^*(f)b(f)}{\mathcal{S}_n(f)} df,
\end{align}
where $\mathcal{S}_n(f)$ is the noise power spectral density (PSD).

% I think we should put a short description of MALA here
Since our likelihood function is coded in 
\subsection{MCMC with Gradient-based sampler}
\label{sec:gradient}

>>>>

\begin{align}
    \log{\mathcal{L}(d|\theta)} = -\left<d-h(\mathbf{\theta})|d-h(\mathbf{\theta})\right>/2,
\label{eq: loglikelihood}
\end{align}
where $d$ is the data, $h(\mathbf{\theta})$ is the strain predicted by a waveform model with a specific set of source parameters.
It is computationally cheaper to compute the likelihood in the frequency domain, which can be defined as 
\begin{align}
    \left<a|b\right> = 4 Re\int \frac{a^*(f)b(f)}{\mathcal{S}_n(f)} df,
\label{eq: innerproduct}
\end{align}
where $\mathcal{S}_n(f)$ is the noise power spectral density (PSD).

\subsection{MCMC with Gradient-based sampler}
\label{sec:gradient}

Given eq. \ref{eq: loglikelihood} and the prior, one can evaluate the posterior
density function over the entire parameter space of interest to obtain the most
probable set of points that are consistent with the data. However, direct
sampling quickly becomes intractable as the dimensionality of the parameter
space increases beyond a few dimensions. Markov chain Monte Carlo (MCMC) is a
common method employed to generate samples when direct sampling is not possible.

In MCMC, the posterior distribution is approximated by a Markov chain that
converges to the target distribution. The Markov chain is constructed by
iteratively proposing a new point in the parameter space based on the current
location of the chain. The proposed point is accepted with a probability that is
usually set to be proportional to the ratio of the posterior density evaluated
at the proposed point and the current point. The chain can either accept the
proposal and move to the new location, or reject the proposal and stay at the
current location. This process is repeated until the chain converges to the
target distribution. The samples generated by the chain are then used to
estimate the quantities of interest, such as the mean and credible intervals of
the source parameters. In practice, since we do not know the target distribution
ahead of time, the MCMC process is usually repeated until a certain criterion is
met, such as a Gelman-Rubin convergence statistic \cite{Gelman-rhat} lower than
a threshold or simply after a certain number of iterations.

Compared to direct sampling, MCMC algorithms only explore regions that are
highly probable, thus reducing the computational cost by not wasting resource in
region where it is unlikely to generate the data.
